Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-07-31 writing/nips_submission/response/EML_response.tex
Further tweaks

\textbf{Architecture \& contributions:} We agree with the reviewers that the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations. We would like to clarify the architecture and training. First we will clarify how a basic polynomial is learned. This is depicted schematically on the right. As in standard meta-learning, we generate a set of examples, consisting of tuples of input point, and the target output (i.e. the polynomial evaluated at that point). The meta-network $\mathcal{M}$ processes this set of (embedded input, embedded target) pairs to produce a function embedding. Specifically, it concatenates each pair, applies two layers of identical processing to each concatenated pair independently, max pools elementwise across them, and then applies two more layers of processing to produce the function embedding $z^{func}$ for this polynomial. We pass the function embedding through the hyper network $\mathcal{H}$ to parameterize a function $F$ which performs the mapping from inputs to outputs. We can then use $F$ to transform a new set of probe inputs (i.e. points we want to evaluate the polynomial at) to produce a set of predictions, and then train or evaluate the model on corresponding targets. \par 

@@

\textbf{The insight of our paper is that learning a meta-mapping over polynomials is exactly analogous to learning a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of embeddings of input polynomials and output polynomials for a meta-mapping that operates over polynomials (e.g. multiplying by 2). Specifically, a set of polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding for each one. We then take a set of pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for the function that transforms one polynomial into another. Just as above, we pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2. We can then pass a novel probe polynomial through $F$ to produce a predicted output, which is the embedding of a novel function obtained by transforming the input polynomial. The only differences from the basic case are: 1) where the inputs and targets come from 2) how the loss or evaluation is computed from the predictions. For basic training, we used an appropriate loss in the output space for each task; in meta training, we used an $\ell^2$ loss between the predicted task embedding and the embedding of the target task. One of the main algorithmic insights of our work is that this loss produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig. 3). To evaluate meta-mapping performance, we actually computed the performance of the predicted output embedding at computing the target polynomial. For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output embedding matched $2x + 4$, by feeding it to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs. We hope this clarifies our approach, and why it is fundamentally different from prior work. All three reviewers highlighted the novelty of considering transformations over tasks. That is the conceptual contribution of our paper, and the algorithmic contribution is to show an approach for solving this challenge, by using the same computational structure for both basic tasks and meta-mappings. Because we use the same networks for both basic tasks and meta-mappings, our approach is parsimonious --- it does not require adding any new parameters to the model. (This actually performs better than having separate networks for basic tasks and meta-mappings, see appendix D.1.) While other meta-learning approaches could potentially be adapted to do meta-mappings, it is unclear that they could be adapted so parsimoniously, or perform well. However, we think exploring alternate approaches, or combining algorithms like MAML with architectures like ours, could be exciting future directions. For now, we are revising the paper to clarify our message. \par 

@@

\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 61.4\% on 5-shot, 5-way classification, competitive with MAML and Meta-LSTM. We expect that with more than a few days to tune and refine the model we could do much better. \par

>>>>

\textbf{Architecture \& contributions:} We agree with the reviewers that the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations. First we clarify how our architecture and training work for learning basic polynomials (see the diagram), then turn to the issue of meta-mappings. As in standard meta-learning, we generate a set of examples, consisting of (input, target) tuples exemplifying the polynomial to be learned. We embed the inputs and targets, then pass them to he meta-network $\mathcal{M}$ which processes them to produce a function embedding. $\mathcal{M}$ concatenates each pair, applies two layers of identical processing to each concatenated pair independently, max pools elementwise across them, and then applies two more layers of processing to produce the function embedding $z^{func}$ for this polynomial. We pass the function embedding through the hyper network $\mathcal{H}$ to parameterize a function $F$ which performs the mapping from inputs to outputs. We can then use $F$ to transform a new set of probe inputs (i.e. points we want to evaluate the polynomial at) to produce a set of predictions, and then train or evaluate the model on corresponding targets. \par 

@@

\textbf{The insight of our paper is to show how both basic tasks and meta-mappings can be treated homogenously, by allowing the network to recurse on its own representations.} To learn a meta-mapping that operates over polynomials (e.g. multiplying by 2), we use example (input, target) tuples, except that now each input or target is an embedding of a polynomial. These embeddings are constructed as above, by passing examples of the polynomial through the meta network $\mathcal{M}$. We then take a set of pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for the function that transforms one polynomial into another. Just as above, we pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2. We can then pass a novel probe polynomial through $F$ to produce a predicted output, which is the embedding of a novel function obtained by transforming the input polynomial. The only differences from the basic case are: 1) where the inputs and targets come from 2) how the loss or evaluation is computed from the predictions. For basic training, we used an appropriate loss in the output space for each task; in meta training, we used an $\ell^2$ loss between the predicted task embedding and the embedding of the target task. One of the main algorithmic insights of our work is that this loss produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig. 3a, held-out mapping, on held-out task). To obtain those results, we actually evaluated the performance of the predicted output embedding at computing the target polynomial. For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output embedding matched $2x + 4$ by feeding it to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs. We hope this clarifies our approach, and why it is fundamentally different from prior work. All three reviewers highlighted the novelty of considering transformations over tasks. That is the conceptual contribution of our paper, and the algorithmic contribution is to show an approach for solving this challenge, by using the same computational structure for both basic tasks and meta-mappings. Because we use the same networks for both basic tasks and meta-mappings, our approach is parsimonious --- it does not require adding any new parameters to the model. (This actually performs better than having separate networks for basic tasks and meta-mappings, see appendix D.1.) While other meta-learning approaches could potentially be adapted to do meta-mappings, it is unclear that they could be adapted so parsimoniously, or perform well. However, we think exploring alternate approaches, or combining algorithms like MAML with architectures like ours, could be exciting future directions. For now, we are revising the paper to clarify our message. \par 

@@

\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 62.4\% on 5-shot, 5-way classification, and 46.9\% on 1-shot, competitive with MAML and Meta-LSTM. We expect that with more than a few days to tune and refine the model we could do better. \par
